\Large \bf 6.824 Final Project

### 2014-05-09 writeup/paper.tex
added some benchmark results to writeup (unformatted)

\subsection{Throughput and Latency}

@@

@@

%{\footnotesize \bibliographystyle{acm}
%\bibliography{paper}}
%\newpage
%\section{\\Appendix A: Alternative Emergency Alert Scheme}
% the \\ insures the section title is centered below the phrase: Appendix B
% See Appendix A for  (NOTE: perhaps the base station could note the empty 
%space, and then take advantage of the periodicity to send a broadcast packet 
%that would allow sensors to opportunistically fill in the blank, thus 
%increasing the success rate).(NOTE: opportunistic make up listed in last note
%could allow for the two sensors to randomly switch to open slots, potentially
% getting rid of the collision state). (NOTE: unless the fill-in-the-blank
%scheme is uses, in which case the base station will be fully aware of any 
%re-mappings as it dictated them in the first place!).
%\newpage
\end{document}

>>>>

\subsection{Throughput and Latency}
Avg client latency w/ out paxos optimizations:
one shard, 3 groups w/ 3 replicas = 15.4ms/op
many shards, 3 groups w/ 3 replicas = 21.8ms/op

Avg client throughput w/ out paxos optimizations:
one shard, 3 groups w/ 3 replicas = 65 requests/second
many shards, 3 groups w/ 3 replicas = 46 requets/second

Client requests per second:
3 groups w/ 3 replicas:
~179 requests per second (saturates at around 50 users)

@@

One notable bottleneck is disk writes. The database library we used,
levedb, uses a cache and is quite fast. However, in the process of
debugging networked RPCs, we implemented simple logging. This logging
slowed down the operations by nearly a factor of ten. This was a good
demonstration of how care must be taken in even the most mundane
aspects, such as logging.

@@

%{\footnotesize \bibliographystyle{acm}
%\bibliography{paper}}
%\newpage
\end{document}
